Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-25 Dissertation/Thesis/tex/results.tex
dissertation final edit done through chap 7.3.2

\subsection{Hardware Configuration}
The Pioneer 3 ground robot (Figure \ref{fig:Pioneer}) is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provide the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

@@

The software structure is similar to ROS nodes Section \ref{sec:Ae2DNumExamples}, which simply involves a mapping node, an exploration node, and a visualization node using OpenGL libraries~\cite{openGL}. The only differences are eliminating the simulator (Stage) and adding synchronization among the sensors, which is of high importance to the proposed occupancy grid mapping approach. Any time delay between the robot pose estimation and the sensor depth readings can cause conflicting information, which may be harmful to the probabilistic map. Thus, ROS approximate message filters are applied such that the pose from Vicon Tracker ($100$Hz) and the Microsoft Kinect ($30$Hz) are nearly synchronized, which provides validity of the assumption that the measurement ray positions and directions are known deterministically.

@@

\begin{figure}
	\centering
    	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_bottom_left_cropped.jpg}
        		\caption{Bottom-left view}
        		\label{fig:Experiment_blv}
    	\end{subfigure}
	\hspace*{0.05\columnwidth}
	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_bottom_right_cropped.jpg}
        		\caption{Bottom-right view}
        		\label{fig:Experiment_brv}
    	\end{subfigure}
\caption{2D Experimental Environment}
	\medskip
	\small
	Images from two perspectives show the walls and obstacles of the experimental environment.
\label{fig:ExpSetupPhoto}
\end{figure}

@@

The autonomous exploration is governed by a policy to maximize expected entropy decreases, so entropy and entropy change with time (Figure \ref{fig:ExperimentH}) are important metrics. In this example, the a priori occupancy probabilities of all cells are $0.1$, so the entropies could temporarily rise for likely occupied cells. The total map entropy begins at roughly $2613$ and decreases by roughly half to $1338$. Many grid cells within the map limits are occluded by walls, preventing the blocked cells from occupancy probability changes. In some cases, the robot is able to update the cell occupancy probabilities; in other cases, cells fall inside regions occluded from all reachable space, and the robot cannot update these cells. Among those grid cells visible from collision-free locations, the vast majority of cells were updated in less than $3$ min while following a very slow ($5$ cm/sec) trajectory.

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_north.jpg}
        		\caption{North Region}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.95\columnwidth}
	\vspace*{0.03\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_south.jpg}
        		\caption{South Region}
    	\end{subfigure}
	\caption{3D Experimental Environment for Level Flight}
	\medskip
	\small
	The 3D experimental environment is designed to resemble a large room within an office building. The walls are build from from cardboard suspended from stanchions and gray sheeting with $80/20$ supports, and miscellaneous objects are placed around the room as well.
	\label{fig:exp3DEnvironment}
\end{figure}

@@

The experimental results show that the robot successfully explores a 3D space, capturing occupied space above and below the robot. The quadrotor does an initial rotation over $20$ sec, then explores the space with planned motions in all three dimensions, shown in Figure \ref{fig:exp3DVid}. The robot generates a 3D probabilistic map (Figure \ref{fig:exp3DOccMap}) and uses this for entropy prediction and collision-free motion planning with a 3D cost map (Figure \ref{fig:Full3DExplorationCostmaps}).

>>>>

\subsection{Hardware Configuration}
The Pioneer 3 ground robot (Figure \ref{fig:Pioneer}) is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provides the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

@@

The software structure is similar to ROS nodes Section \ref{sec:Ae2DNumExamples}, which simply involves a mapping node, an exploration node, and a visualization node using OpenGL libraries~\cite{openGL}. The only differences are eliminating the simulator (Stage) and adding synchronization among the sensors, which is of high importance to the proposed occupancy grid mapping approach. Any time delay between the robot pose estimation and the sensor depth readings can cause conflicting information, which may be harmful to the probabilistic map. Thus, ROS Message Filters are applied such that the pose from Vicon Tracker ($100$ Hz) and the Microsoft Kinect ($30$ Hz) are nearly synchronized, which provides validity of the assumption that the measurement ray positions and directions are known deterministically.

@@

\begin{figure}
	\centering
    	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_bottom_left_cropped.jpg}
        		\caption{Bottom-Left View}
        		\label{fig:Experiment_blv}
    	\end{subfigure}
	\hspace*{0.05\columnwidth}
	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_bottom_right_cropped.jpg}
        		\caption{Bottom-Right View}
        		\label{fig:Experiment_brv}
    	\end{subfigure}
\caption{2D Experimental Environment}
	\medskip
	\small
	Images from two perspectives show the walls and obstacles of the experimental environment.
\label{fig:ExpSetupPhoto}
\end{figure}

@@

The autonomous exploration is governed by a policy to maximize expected entropy decreases, so entropy and entropy change with time (Figure \ref{fig:ExperimentH}) are important metrics. In this example, the a priori occupancy probabilities of all cells are $0.1$, so the entropies could temporarily rise for likely occupied cells. The total map entropy begins at roughly $2613$ and decreases by roughly half to $1338$. Many grid cells within the map limits are occluded by walls, preventing the blocked cells from occupancy probability changes. In some cases, the robot is able to update the cell occupancy probabilities; in other cases, cells fall inside regions occluded from all reachable space, and the robot cannot update these cells. Among those grid cells visible from collision-free locations, the vast majority of cells are updated in less than $3$ min while following a very slow ($5$ cm/sec) trajectory.

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_north.jpg}
        		\caption{North Region}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.95\columnwidth}
	\vspace*{0.03\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_south.jpg}
        		\caption{South Region}
    	\end{subfigure}
	\caption{3D Experimental Environment for Level Flight}
	\medskip
	\small
	The 3D experimental environment is designed to resemble a large room within an office building. The walls are built from from cardboard suspended from stanchions and gray sheeting with $80/20$ supports, and miscellaneous objects are placed around the room as well.
	\label{fig:exp3DEnvironment}
\end{figure}

@@

The experimental results show that the robot successfully explores a 3D space, capturing occupied space above and below the robot. The quadrotor does an initial rotation over $20$ sec, then explores the space with planned motions in all three dimensions, shown in Figure \ref{fig:exp3DVid}. The robot generates a 3D probabilistic map (Figure \ref{fig:exp3DOccMap}) and uses this for entropy prediction and collision-free motion planning with a 3D cost map (Figure \ref{fig:Full3DExplorationCostmaps}). A video of this experiment is available at \href{https://www.youtube.com/watch?v=2Q2_-d8kNu0}{\WriteBlue{https://www.youtube.com/watch?v=2Q2\_-d8kNu0}}.
